---
output:
  md_document:
    variant: gfm

---
<p align="justify">    

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = F}
library(patchwork)
knitr::opts_chunk$set(echo = TRUE)
```

In Experiment 1, we're looking at differences in the microbiome between coffee drinkers and non-coffee drinkers. 
```{r, warning=FALSE, cache = T}
source("scripts/ex1_baseline_differences_CD_vs_NCD.R")
```

```{r, warning=FALSE, fig.width = 16, fig.height = 8}
ex1pca + ex1alpha / ex1DA + plot_layout(guides = 'collect')

ex1DA_metab
```

In Experiment 2, we're looking at differences in the microbiome between coffee drinkers and non-coffee drinkers. 
```{r, warning=FALSE, cache = T}
source("scripts/ex1_baseline_differences_CD_vs_NCD.R")
```

```{r, warning=FALSE, fig.width = 16, fig.height = 8}
ex1pca + ex1alpha / ex1DA + plot_layout(guides = 'collect')

ex1DA_metab
```



In Experiment 2B, we're looking at features that return to non-coffee drinker levels post washout (coffee abstinence). 
```{r, warning=FALSE, cache = T}
source("scripts/ex_RESTORATION_coffee_analysis_post_washout_normalisation.R")
```

```{r, warning=FALSE, fig.width = 16, fig.height = 8}
ex_RESTpca + ex_RESTalpha / ex_RESTDA + plot_layout(guides = 'collect')

ex_REST_DA_metab
```


In Experiment 3, we're looking at the effects of going back on either caffeinated or decaffeinated coffee post-washout (coffee abstinence). 
```{r, warning=FALSE, cache = T}
source("scripts/ex3_intervention_v3_vs_v4.R")
```


```{r, warning=FALSE, fig.width = 16, fig.height = 8}
ex3pca + ex3alpha + plot_layout(guides = 'collect')

ex3metab
```