---
output:
  md_document:
    variant: gfm

---
<p align="justify">    

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = F}
library(patchwork)
knitr::opts_chunk$set(echo = TRUE)
```

In Experiment 1, we're looking at differences in the microbiome between coffee drinkers and non-coffee drinkers. 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex1_baseline_differences_CD_vs_NCD.R")
```

```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 8}
ex1pca + ex1alpha / ex1DA + plot_layout(guides = 'collect')
```
```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 12}
ex1_metab_forest_a + ex1_metab_forest_b  + plot_layout(guides = 'collect') + plot_annotation(title = "Differentially abundant faecal metabolites between non-coffee drinkers (L) and coffee drinkers (R)") 
```

In Experiment 2B, we're looking at features that return to non-coffee drinker levels post washout (coffee abstinence). 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex_RESTORATION_coffee_analysis_post_washout_normalisation.R")
```

```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 8}
ex_RESTpca + ex_RESTalpha / ex_RESTDA + plot_layout(guides = 'collect')
```

```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 12}
ex_REST_metab_forest_a + ex_REST_metab_forest_b + plot_layout(guides = 'collect') + plot_annotation(title = "Differentially abundant faecal metabolites between non-coffee drinkers and coffee drinkers post-washout vs baseline coffee drinker levels")

```


In Experiment 3, we're looking at the effects of going back on either caffeinated or decaffeinated coffee post-washout (coffee abstinence). 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex3_intervention_v3_vs_v4.R")
```


```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 8}
ex3pca + ex3alpha + plot_layout(guides = 'collect')

ex3metab
```

In this additional microbiome experiment, we're looking at the acute effects of coffee abstinence (coffee withdrawal). 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex_washout_acute_withdrawal.R")
```


```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 12}
ex_withdrawpca + ex_withdrawalpha + plot_layout(guides = 'collect')

```


In this additional microbiome experiment, we're looking at the acute effects of going back on either caffeinated or decaffeinated coffee post-washout (coffee abstinence). 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex_INTERVENTION_acute_recaf_or_decaf.R")
```


```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 24}
ex_INTERVENTIONpca + ex_INTERVENTIONalpha + ex_INTERVENTIONDA_GBM + ex_INTERVENTIONDA_GMM +  plot_layout(guides = 'collect', heights = c(1,1,2,2))

```