---
output:
  md_document:
    variant: gfm

---
<p align="justify">    

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = F}
library(patchwork)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev = 'svg') # set output device to svg

```

In Experiment 1, we're looking at differences in the microbiome between coffee drinkers and non-coffee drinkers. 
```{r, warning=FALSE, message = FALSE}
source("scripts/ex1_baseline_differences_CD_vs_NCD.R")
```

```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 12}
(ex1pca | (ex1alpha / ex1DA)) / 
  ((ex1_cyta  + ex1_cytb  + ex1_metab_forest) + plot_layout(widths = c(1,1,5))) + plot_layout(heights = c(2,3))
```

In Experiment 2, we're looking at features that return to non-coffee drinker levels post washout (coffee abstinence). 
```{r, warning=FALSE, message = FALSE}
source("scripts/ex_2_acute_and_full_withdrawal.R")
```

```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 14}
(ex_RESTpca + (ex_RESTalpha/ex_RESTDA)) / (ex_REST_metab_forest_a + ex_REST_metab_forest_b)  + plot_layout(heights = c(2,3))
```


In Experiment 3, we're looking at the effects of going back on either caffeinated or decaffeinated coffee post-washout (coffee abstinence). 

In this additional microbiome experiment 3B, we're looking at the acute effects of going back on either caffeinated or decaffeinated coffee post-washout (coffee abstinence). 
```{r, warning=FALSE, message = FALSE, cache = T}
source("scripts/ex_3_intervention_acute_and_full_recaf_or_decaf.R")
```


```{r, warning=FALSE, message = FALSE, fig.width = 16, fig.height = 30}
((ex_INTERVENTIONpca | ex_INTERVENTIONalpha) + plot_layout(widths = c(2,1), guides = 'collect')) / 
  (GBM_b  + plot_spacer() + GBM_a + plot_layout(guides = 'collect', widths = c(5,1,5))) /
  (GMM_b  + plot_spacer() + GMM_a + plot_layout(guides = 'collect', widths = c(5,1,5))) / ex3metab +  plot_layout(heights = c(3,4,1, 1)) 

```